The LSST-DESC 3x2pt Tomography Optimization Challenge

### 2021-09-01 paper/paper.tex
remove old text
citation updates

%\accepted{}
%\submitjournal{the Astrophysical Journal Supplement}

@@

We use a Gaussian estimate for the covariance \citep{takada_jain}; this also incorporates the number of galaxies in the
sample:
\begin{equation}
    \mathrm{Cov}(C^{ij}_\ell, C^{mn}_\ell) = \frac{1}{(2 \ell + 1)\Delta\ell f_\mathrm{sky}}(D^{im}_\ell  D^{jn}_\ell + D^{in}_\ell D^{jm}_\ell)
\end{equation}
where $D^{ij}_\ell = C^{ij}_\ell + N^{ij}_\ell$, $\Delta_\ell$ is the size in $\ell$ of the binned spectra, and we assume an $f_\mathrm{sky}=0.25$.  The noise spectra are:
\begin{align}
N^{\mathrm{clust},ij}_\ell = \delta_{ij} / n_i \\
N^{\mathrm{lens},ij}_\ell = \delta_{ij} \sigma_e^2 / n_i
\end{align}
where $n_i$ is the angular number density of galaxies in bin $i$ (we asssume equally weighted galaxies, and a 
total number density over all bins of 20 galaxies per square arcminute) and $\sigma_e=0.26$, roughly matching that found in previous surveys \citep{des,kids,hsc}.

@@

%During the training stage of the algorithm GPz is inferring the locations and
%spreads that describe the basis functions; during the validation stage it is
%inferring the appropriate complexity of the model, essentially how many basis
%functions to use.

@@

%GPz requires very little fine-tuning. The most important parameter is $m$, the number of basis functions. A higher $m$ corresponds to higher model complexity and longer training times.

@@

%\subsection{ {\sc NeuralNetwork 2} }

>>>>

@@

We use a Gaussian estimate for the covariance \citep{takada_jain}; this also incorporates the number of galaxies in the
sample:
\begin{equation}
    \mathrm{Cov}(C^{ij}_\ell, C^{mn}_\ell) = \frac{1}{(2 \ell + 1)\Delta\ell f_\mathrm{sky}}(D^{im}_\ell  D^{jn}_\ell + D^{in}_\ell D^{jm}_\ell)
\end{equation}
where $D^{ij}_\ell = C^{ij}_\ell + N^{ij}_\ell$, $\Delta_\ell$ is the size in $\ell$ of the binned spectra, and we assume an $f_\mathrm{sky}=0.25$.  The noise spectra are:
\begin{align}
N^{\mathrm{clust},ij}_\ell = \delta_{ij} / n_i \\
N^{\mathrm{lens},ij}_\ell = \delta_{ij} \sigma_e^2 / n_i
\end{align}
where $n_i$ is the angular number density of galaxies in bin $i$ (we asssume equally weighted galaxies, and a 
total number density over all bins of 20 galaxies per square arcminute) and $\sigma_e=0.26$, roughly matching that found in previous surveys \citep{des,desy3a,desy3b,kids,hsc}.

@@

@@

@@
